Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2015-09-17 gel_cond/trunk/paper.tex
describe fig:breaking b and c

>>>>

$L$ is a good measure of the significance of a bond breaking event. Small values indicate a local rearrangement whereas large values are the signature of important changes in the topology of the network, namely strand rupture. Figure~\ref{fig:breaking}b shows the distribution of $L$ for three colloidal volume fractions. Excluding the largest values that are dominated by the limited size of the field of view, $L$ seems to follow a power-law distribution of exponent between $-3$ and $-4$. However the values at $L=1$ seems in excess. Figure~\ref{fig:breaking}c compares the probability distribution of $q_2$ for all bond breaking events versus for evens with $L>1$. In both cases bonds about to break have a higher probability of being under tension, but this trend is much clearer when excluding local events. Both observations point to spurious detection of bond breaking events due to localisation errors comparable to the short attraction range and rattling of particles. For this reason, but also to focus on topologically relevant strand rupture, we discard all events with $L<4$ in the following analysis.
